---
title: "p8105_hw1_kw3041"
output: github_document
date: "2025-09-21"
---

## Homework 1 

Below, I will be loading packages and dataset needed for solving the homework 1. 

```{r}
library(moderndive)
data("early_january_weather")
```

In order to answer the first question, I am going to take a look at the dataset to assess it. 

```{r}
head(early_january_weather)
```

## Problem 1. 

This data includes variables such as `temp`, which is measured in Fahrenheit; `dewp` which is a measure of dewpoint; `humid` for relative humidity; `wind_speed`, and a couple more variables. 

## Checking the structure of "early_january_weather" tibble: 

The early_january_weather dataset contains following number of rows: 
```{r}
nrow(early_january_weather)
```

The early-january_weather dataset contains the following numner of columns:
```{r}
ncol(early_january_weather)
```

The mean temperature of this dataset is:
```{r}
mean(early_january_weather[["temp"]], na.rm = TRUE)
```

## Plot of the weather 

In this portion I am going to access ggplot from ggplot2 package by using function `::`. Below can be found a scatterplot of Temperature vs. Time, colored by Humidity. 

```{r}
weather_plot = ggplot2::ggplot(
  early_january_weather,
  ggplot2::aes(x = time_hour, y = temp, color = humid)
) +
  ggplot2::geom_point(alpha = 0.5) + 
  ggplot2::labs(
    title = "Temperature over Time; Colored by Humidity",
    x = "Time (hour)",
    y = "Temperature (F)",
    color = "Humidity"
  ) + 
    ggplot2::theme_minimal()

weather_plot
```

This is a R inline that will save the plot as a png. 

```{r}
ggplot2::ggsave("scatterplot_weather.png", plot = weather_plot, width = 10, height = 8)
```




## Problem 2 

First, I will set a random numeric sample.


```{r}
set.seed(123)
numeric_vec = rnorm(10)
```

```{r}
logical_vec = numeric_vec > 0
```

```{r}
char_vec = letters[1:10]
```

```{r}
factor_vec = factor(sample(c("Low", "Medium", "High"), size = 10, replace = TRUE ))
```

```{r}
df = data.frame(
  numeric_var = numeric_vec,
  logical_var = logical_vec,
  char_var = char_vec,
  factor_var = factor_vec
)

df
```


# Numeric and Logical Mean
Now, I will be taking mean from each variable: 

```{r}
mean(df[ , "numeric_var"])
mean(df[ , "logical_var"])
```

